---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# ArchaeaCentre

<!-- badges: start -->
[![GitHub issues](https://img.shields.io/github/issues/richardstoeckl/archaeacentre)](https://github.com/richardstoeckl/archaeacentre/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/richardstoeckl/archaeacentre)](https://github.com/richardstoeckl/archaeacentre/pulls)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- [![Bioc release status](http://www.bioconductor.org/shields/build/release/bioc/archaeacentre.svg)](https://bioconductor.org/checkResults/release/bioc-LATEST/archaeacentre) -->
<!-- [![Bioc devel status](http://www.bioconductor.org/shields/build/devel/bioc/archaeacentre.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/archaeacentre) -->
<!-- [![Bioc downloads rank](https://bioconductor.org/shields/downloads/release/archaeacentre.svg)](http://bioconductor.org/packages/stats/bioc/archaeacentre/) -->
<!-- [![Bioc support](https://bioconductor.org/shields/posts/archaeacentre.svg)](https://support.bioconductor.org/tag/archaeacentre) -->
<!-- [![Bioc history](https://bioconductor.org/shields/years-in-bioc/archaeacentre.svg)](https://bioconductor.org/packages/release/bioc/html/archaeacentre.html#since) -->
<!-- [![Bioc last commit](https://bioconductor.org/shields/lastcommit/devel/bioc/archaeacentre.svg)](http://bioconductor.org/checkResults/devel/bioc-LATEST/archaeacentre/) -->
<!-- [![Bioc dependencies](https://bioconductor.org/shields/dependencies/release/archaeacentre.svg)](https://bioconductor.org/packages/release/bioc/html/archaeacentre.html#since) -->
[![check-bioc](https://github.com/richardstoeckl/archaeacentre/actions/workflows/check-bioc.yml/badge.svg)](https://github.com/richardstoeckl/archaeacentre/actions/workflows/check-bioc.yml)
[![Codecov test coverage](https://codecov.io/gh/richardstoeckl/archaeacentre/graph/badge.svg)](https://app.codecov.io/gh/richardstoeckl/archaeacentre)
<!-- badges: end -->

This package provides default plots and functions that are used internally at the German Archaea Centre in Regensburg.

## Installation instructions

Get the latest stable `R` release from [CRAN](http://cran.r-project.org/). Then install the development of `archaeacentre` from [GitHub](https://github.com/richardstoeckl/archaeacentre) with:

```{r 'install_dev', eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
    install.packages("BiocManager")
}

BiocManager::install(c("remotes", "richardstoeckl/archaeacentre"))
```

## Citation

Below is the citation output from using `citation('archaeacentre')` in R. Please
run this yourself to check for any updates on how to cite __archaeacentre__.

```{r 'citation', eval = requireNamespace('archaeacentre')}
print(citation("archaeacentre"), bibtex = TRUE)
```

Please note that the `archaeacentre` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

## Development tools

* Continuous code testing is possible thanks to [GitHub actions](https://www.tidyverse.org/blog/2020/04/usethis-1-6-0/)  through `r BiocStyle::CRANpkg('usethis')`, `r BiocStyle::CRANpkg('remotes')`, and `r BiocStyle::CRANpkg('rcmdcheck')` customized to use [Bioconductor's docker containers](https://www.bioconductor.org/help/docker/) and `r BiocStyle::Biocpkg('BiocCheck')`.
* The [documentation website](http://richardstoeckl.github.io/archaeacentre) is automatically updated thanks to `r BiocStyle::CRANpkg('pkgdown')`.
* The code is styled automatically thanks to `r BiocStyle::CRANpkg('styler')`.
* The documentation is formatted thanks to `r BiocStyle::CRANpkg('devtools')` and `r BiocStyle::CRANpkg('roxygen2')`.

For more details, check the `dev` directory.

This package was developed using `r BiocStyle::Biocpkg('biocthis')`.


