---
title: "Introduction to the archaeacentre package"
author: 
  - name: Richard Stöckl
    affiliation:
    - Archaea Centre Regensburg
    email: richard.stoeckl@ur.de
output: 
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: show
date: "`r doc_date()`"
package: "`r pkg_ver('archaeacentre')`"
vignette: >
  %\VignetteIndexEntry{Introduction to archaeacentre}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    crop = NULL ## Related to https://stat.ethz.ch/pipermail/bioc-devel/2020-April/016656.html
)
```

# Basics

## Install `archaeacentre`

`R` is an open-source statistical environment which can be easily modified to enhance its functionality via packages. `r Biocpkg("biocthis")` is a `R` package available via the [Github](https://github.com/richardstoeckl/archaeacentre) repository.

Get the latest stable `R` release from [CRAN](http://cran.r-project.org/). Then install the development of `archaeacentre` from [GitHub](https://github.com/richardstoeckl/archaeacentre) with:

```{r 'install_dev', eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
    install.packages("BiocManager")
}

BiocManager::install("richardstoeckl/archaeacentre")
```

# Plot a basic growth curve

```{r 'load data', eval = TRUE, echo = TRUE}
# 1. load the package
library(archaeacentre)

# 2. load some test data included with the package
testData <- archaeacentre::growthData

# 3. plot the growth curves in their most basic way, with the presets for "robert":
archaeacentre::plotGrowthCurve(testData, timepoint, concentration, grouping = c("timepoint", "organism"), organism, type = "robert")
```

# Modify your growth curve plot

Since the `plotGrowthCurve` function is basically just a wrapper around a ggplot2 plot with some default settings, you can modify the plot to your liking. Here is one example:

```{r 'load data', eval = TRUE, echo = TRUE}
library(ggplot2)

archaeacentre::plotGrowthCurve(testData, timepoint, concentration, grouping = c("timepoint", "organism"), organism, type = "robert") +
    ggplot2::labs(title = "Growth curve of some test data", x = "Timepoint after inocculation in [h]", y = "Concentration in [cells/mL]") +
    ggplot2::guides(color = guide_legend(title = "Species"))
```


